\documentclass[pdftex,letterpaper,11pt]{article}%
\usepackage[export]{adjustbox}
\usepackage{multirow}
\usepackage[arabicsections]{dpugatex}
%\usepackage{dpppl}
%\usepackage{lscape}
\usepackage{pdflscape}
\usepackage{longtable}

\usepackage{tikz}

\usepackage[british]{babel}
\usepackage{amssymb,amsmath,warpcol,url,ctable,multirow,caption,threeparttable,float,soul,gensymb}
%\usepackage[noend]{algpseudocode}
\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother


\usepackage{subcaption}


\usepackage{xcolor,colortbl}%Per colorejar cel·les de les taules
\definecolor{verylightgray}{gray}{0.90}
\newcommand{\verylightgray}[1]{\cellcolor{verylightgray}#1}


\usepackage{arydshln} %Per dashed lines
\setlength\dashlinedash{1.5pt}
\setlength\dashlinegap{2.5pt}
\setlength\arrayrulewidth{0.8pt}

\usepackage[utf8]{inputenc}
\usepackage{eurosym}
\usepackage{soul}
\setstcolor{red} % Tatxat vermell pel text a eliminar!!!!
\definecolor{lightgreen}{rgb}{0.564706,0.933333,0.564706}
\newcommand{\miquel}[1]{{\sethlcolor{lightgreen} \hl{#1}} } % To highlight with light green Miquel's comments.
\soulregister\citet7 % These \soulregister commands allow us to avoid problems between soul functions (\hl, \st, ...) and these other functions (\citet,\citep,\ref,\footnote, ...). Include more if it is necessary.
\soulregister\citep7
\soulregister\cite7
\soulregister\ref7
\soulregister\footnote7
\soulregister\textit7
\soulregister\textbf7
\soulregister\textsc7
\soulregister\`7 % for open accents.
\soulregister\'7 % for closed accents.
\soulregister\% 7 % for \%age symbol
\usepackage{tabularx,tabulary}
\usepackage[osf]{mathpazo} % Amb aquest paquet faig ús de la lletra Palatino, la que fan servir Puga, Duranton et al. Amb l'opció [osf] la numeració és "old fashion", però és incompatible amb un títol en negreta i small caps (desapareixen les small caps!). Per tant, per ara opto per NO aplicar aquesta opció.
\usepackage[abs]{overpic}

\usepackage{hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks=true, breaklinks=true, citecolor= darkblue, linkcolor=blue, urlcolor=blue}

\usepackage{chngcntr}

\newcommand{\mc}[3]{\multicolumn{#1}{#2}{#3}}
\newcommand{\mcc}[1]{\multicolumn{1}{c}{#1}}
\newcommand{\mcb}[1]{\multicolumn{1}{c}{\bf #1}}

\newcommand{\mr}[3]{\multirow{#1}{#2}{#3}} % Per fer Files múltiples (seguint el punt de vista de les columnes múltiples.
\newcommand{\mg}[3]{\multicolumn{#1}{#2}{\verylightgray #3}} %Combino el color de les cel·les amb al command de les columnes múltiples.



%\hypersetup{%
 % pdftitle={Race and neighborhoods in the 21$^{\text{st}}$ century},%
 % pdfauthor={Jorge De la Roca (NYU) , Ingrid Gould Ellen (NYU) and Katherine O'Regan (NYU)},%
 % pdfkeywords={race segregation, discrimination}}
%\pdfOpenFitWidth
%\pdfShowBookmarks

\onehalfspacing%
%\doublespacing%

\newenvironment{tablenote}[1]{\begin{list}{}{\vskip-5mm\relax
\setlength{\leftmargin}{#1} \setlength{\rightmargin}{\leftmargin}}
\item[]\footnotesize\vskip-7pt
{\em Notes}:\space\ignorespaces}{\end{list}}

\newcommand{\jdlradded}[1]{#1}
\newcommand{\dpadded}[1]{#1}
\newcommand{\jdlrdeleted}[1]{}
\newcommand{\dpdeleted}[1]{}
\newcommand{\jdlrcomment}[1]{}
\newcommand{\dpcomment}[1]{}
\newcommand{\comment}[1]{}
\newcommand{\martin}[1]{{\color{blue} Martin: [{#1}]}}
\newcommand{\dani}[1]{{\color{purple} Dani: [{#1}]}}

\begin{document}
\begin{titlepage}
\vspace*{1ex}
\begin{minipage}{\textwidth}
\begin{center}%

    {\textsb{\LARGE Spatial Signatures\\ \textit{Understanding (urban) spaces
    through form and function}}}\\[4ex]%


{\Large\textbf{Daniel Arribas-Bel}\footnote[1]{THANKS.}\footnote[2]{Geographic
Data Science Lab, Department of Geography and Planning, University of
Liverpool, Roxby Building , 74 Bedford St S , Liverpool , L69 7ZT, United
Kingdom}\footnote[3]{E-mail: \url{D.Arribas-Bel@liverpool.ac.uk}; phone: +44 (0)151 795 9727; website: \url{http://darribas.org}.
}}\\[1mm]
%
{\Large\textsb{Martin Fleischmann}\footnotemark[1]\footnotemark[2]\footnote[4]{
E-mail: \url{M.Fleischmann@liverpool.ac.uk}; website: \url{https://martinfleischmann.net/}.}}\\[1mm]
{\large\textit{Geographic Data Science Lab, University of Liverpool} }\\[2.5ex]
%
July 2021\vspace{1.5ex}
%
\end{center}
%
\begin{abstract}
% Punchy intro
        This paper presents the notion of spatial signatures as a
        characterisation of space based on form and function designed to
        understand urban environments.
% Background - What
The spatial organisation of the different components of cities is relevant
for at least two main reasons.
%
On
the one hand, it encodes many aspects of the phenomena
that created such an arrangement in the first place. On the other, once in
place, this arrangement of urban form and function underpins many
outcomes, from economic productivity to environmental sustainability.
% Proposal - How
Our approach unfolds in three main stages.
%% ET
First, we propose a new spatial unit --the Enclosed Tessellation (ET) cell-- to
delineate space in a way that is exhaustive and matches the underlying
processes at which urban form and function operate.
%% Build F&F
Second, we propose to attach a large variety of form and function-based
characters to ET cells to describe each of these units.
%% Clustering
Third, to build spatial signatures, information on ET cells can be clustered
using unsupervised learning techniques.
%% Result
This process results in a theory-informed, data-driven
typology of space that follows form and function.
% Illustration
We illustrate this approach by applying it to a sample of five very different
cities scattered across the world. Our results demonstrate the ability to
successfully differentiate different parts of a city that were built at
different points in time and under different technological regimes, but also
highlight broader comparisons about the nature of urban fabric in different
regions.
% Benefits - Why
Our contribution resides in leveraging modern data, technology and methods to propose a
detailed, consistent and scalable methodology that characterises urban form and
function.
%
The spatial signatures can be used across academic disciplines and by a variety of
practitioners and policymakers supporting initiatives such as the Sustainable
Development Goals.
\end{abstract}
%
\vspace{1.5ex}
%
Key words: \hskip.25em Geographic Data Science, Urban Form, Urban Function\\
%
\vspace*{-1.5ex}
%
\end{minipage}
\end{titlepage}

% Section 1 - Intro
\input{ss_1.tex}

% Section 2 - FF
\input{ss_2.tex}

% Section 3 - SS
\input{ss_3.tex}

\input{ss_3a.tex}

\input{ss_3b.tex}

\input{ss_3c.tex}

% Section 4 - Empirics
\input{ss_4.tex}

% Section 5 - Conclusion
\input{ss_5.tex}

\clearpage




\bibliographystyle{apalike}
\bibliography{refs}

\clearpage

\input{ss_appendix.tex}

\clearpage

\end{document}
